Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest

\begin{code}
\begin{verbatim}
$ ./cxl triangle.cxl
#states = 13
no issues found
$
\end{verbatim}
\end{code}

Essentially, the $\texttt{choose}(S)$
operator provides the input to the program by selecting some value from the
set~$S$, while the $\texttt{assert}$ statement checks that the output is
correct.  If the program is correct, the output of CXL is the size of the
``state graph'' (13 states in this case).  If not, CXL also
reports what went wrong, typically by displaying a summary of an execution in
which something went wrong.

@@

Compiling the code in Figure~\ref{fig:inc} results in the CXL machine code
listed in Figure~\ref{fig:inccode}.
The CXL machine is predominantly a \emph{stack machine}.
All instructions are atomically executed.
Most instructions pop values from the stack or push values onto the stack.
Initially there is one process (with name tag \texttt{\_\_init\_\_/()}
that starts executing at instruction 0 and keeps executing until the last
execution in the program to initialize the state.
In this case, the first instruction is a \texttt{JUMP} instruction that sets the
program counter to 39.
At program counter 1 is the code for the \texttt{incrementer} method.
All methods start with a \texttt{Frame} instruction and end with a \texttt{Return}
instruction.

>>>>

\begin{code}
\begin{verbatim}
$ cxl triangle.cxl
#states = 13
no issues found
$
\end{verbatim}
\end{code}

(For this to work, make sure \texttt{cxl} is in your command shell's search path.)
Essentially, the $\texttt{choose}(S)$
operator provides the input to the program by selecting some value from the
set~$S$, while the $\texttt{assert}$ statement checks that the output is
correct.  If the program is correct, the output of CXL is the size of the
``state graph'' (13 states in this case).  If not, CXL also
reports what went wrong, typically by displaying a summary of an execution in
which something went wrong.

@@

Compiling the code in Figure~\ref{fig:inc} results in the CXL machine code
listed in Figure~\ref{fig:inccode}.
You can obtain this code by invoking \texttt{cxl} with the \texttt{-a} flag
like so:
\begin{code}
\begin{verbatim}
cxl -a Up.cxl
\end{verbatim}
\end{code}
The CXL machine is predominantly a \emph{stack machine}.
All instructions are atomically executed.
Most instructions pop values from the stack or push values onto the stack.
Initially there is one process (with name tag \texttt{\_\_init\_\_/()}
that starts executing at instruction 0 and keeps executing until the last
execution in the program to initialize the state.
In this case, the first instruction is a \texttt{JUMP} instruction that sets the
program counter to 39.
At program counter 1 is the code for the \texttt{incrementer} method.
All methods start with a \texttt{Frame} instruction and end with a \texttt{Return}
instruction.
